### 2021-03-31 written/eLifeRevision/Bittner_eLife2020.tex
finished methods section

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC4/figSC4.pdf}
\end{center}
\caption{\small (SC4):  \textbf{A}. Shows how eigvals change throughout blah
}
\label{fig:SC4}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC5/figSC5.pdf}
\end{center}
\caption{\small (SC5): 
\textbf{A}. Response of each parameter regime to optogenetic silencing during the delay period.
\textbf{B}. Connectivity eigenvalues versus the task error induced by delay period inactivation.
\textbf{C}. Error induced by delay period inactivation with increasing optogenetic strength.  Means and standard deviations are calculated across the entire EPI posterior.
}
\label{fig:SC5}
\end{figure}

@@

To make sense of this inferred distribution, we identified two modes used to represent the two regimes of connectivity in this posterior:
\begin{equation}
\begin{split}
\mathbf{z}_1 = &\argmax_{\mathbf{z}} \log q_{\bm{\theta}}(\mathbf{z} \mid \mathcal{X}) \\
&\text{s.t. }  hw = -1.25\text{, }  sW > 0
\end{split}
\end{equation}
and 
\begin{equation}
\begin{split}
\mathbf{z}_2 = &\argmax_{\mathbf{z}} \log q_{\bm{\theta}}(\mathbf{z} \mid \mathcal{X}) \\
&\text{s.t. } hw = -1.25\text{, } sW < 0
\end{split}
\end{equation}

To understand the connectivity mechanisms governing task accuracy, we took the eigendecomposition of the symmetric connectivity matrices $W = V\Lambda V^{-1}$, which results in the same basis vectors $\mathbf{v}_i$ for all $W$ parameterized by $\mathbf{z}$ (Fig. \ref{fig:SC3}A). 
These basis vectors have intuitive roles in processing for this task, and are accordingly named the \textit{all} mode - all neurons co-fluctuate, \textit{side} mode - one side dominates the other, \textit{task} mode - the Pro or Anti populations dominate the other, and \textit{diag} mode - Pro- and Anti-populations of opposite hemispheres dominate the opposite pair. 
We found significant trends across the EPI posterior connectivities: the eigenvalues $\lambda_{\text{task}}$ and $\lambda_{\text{diag}}$ were correlated with $p_P$, while $\lambda_{\text{all}}$ was anticorrelated with $p_P$.
$\lambda_{\text{all}}$, $\lambda_{\text{side}}$, and $\lambda_{\text{diag}}$ were all significantly anticorrelated with $p_A$.

Under this decomposition, we can re-visualize the posterior in eigenvalue space (Fig. \ref{fig:SC4}).
Furthermore, we can project the dimensions of sensitivity into eigenvalue space as well, giving us a more intuitive sense of how connectivity affects computation in each regime.
We see that sensitivity dimensions $\mathbf{v}_1$ and $\mathbf{v}_2$, which cause $p_P$ to increase and a regime dependent change in $p_A$, both point in the direction of increasing $\lambda_{\text{side}}$ and decreasing $\lambda_{\text{task}}$.
These eigenvalue changes are evident in the simulations of connectivity perturbations away from the modes (Fig. \ref{fig:SC2}).
As the component of connectivity along $\mathbf{v}_1$ and $\mathbf{v}_2$ becomes stronger (left-to-right), there is less separation between Pro an Anti populations (lower $\lambda_{\text{task}}$) and greater separation between Left and Right populations following stimulus presentation (greater $\lambda_{\text{side}}$).
A key differentiating factor is that $\mathbf{v}_1$ substantially increases $\lambda_{\text{diag}}$, while $\mathbf{v}_2$ does not.

\textbf{OPTO} \\
During periods of optogenetic inactivation, activity was decreased proportional to the optogenetic strength $\gamma$
\begin{equation}
x_\alpha = (1-\gamma)\phi(u_\alpha).
\end{equation}

During optogenetic silencing simulations, activations $x_\alpha(t)$ were set to a fraction of their values ($1 - \gamma$), where $\gamma$ is the optogenetic perturbation strength.
We found that $\lambda_{\text{all}}$ and $\lambda_{\text{diag}}$ were significantly anticorrelated with Anti error during delay period inactivation.
Delay period inactivation was from $0.8 < t < 1.2$, choice period inactivation was for $t > 1.2$ and total inactivation was for the entire trial.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC4/figSC4.pdf}
\end{center}
\caption{\small (SC4):  \textbf{A}. The individual parameters of each mode throughout the two regimes.
\textbf{B}. The individual sensitivites of parameters of each mode throughout the two regimes.
}
\label{fig:SC4}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC5/figSC5.pdf}
\end{center}
\caption{\small (SC5): 
\textbf{A}. Response of each parameter regime to optogenetic silencing during the delay period.
\textbf{B}. Error induced by delay period inactivation with increasing optogenetic strength.  Means and standard deviations are calculated across the entire EPI posterior.
}
\label{fig:SC5}
\end{figure}

@@

The EPI distribution of SC model connectivites producing rapid task switching has interesting structure.
Throughout $q_{\bm{theta}}(\mathbf{z} \mid \mathcal{X})$, we see that the probability distribution is narrow in $hW$ (Fig. \ref{fig:SC}C).
This suggests that rapid task switching is sensitive to changes in $hW$, but this is only a single parameter.
The local structure of the distribution varies across parameter space, and thus the nature in which parameter combinations affect rapid task switching.
From visual inspection, we may hypothesize that there are two distinct regimes, most easily visualized in the $sW$-$hW$ marginal distribution: one where $sW$ and $hW$ are correlated for greater $sW$ and one where $sW$ and $hW$ are anticorrelated for lesser $sW$.

We sought two sets of parameters in this distribution representative of each regime, so that we could assess their implications on computation.
For fixed values of $hW$, we hypothesized that there are two modes: one in each regime of greater and lesser $sW$.
To begin, we found one mode for each regime at $hW_{\text{fixed}} = -1.5$ using 200 steps of gradient ascent of the deep probability distribution $q_{\bm{\theta}}(\mathbf{z} \mid \mathcal{X})$.
In regime 1, the initialization had positive $sW$, and the initialization had negative $sW$ in regime 2, which led to disparate modes (Fig. \ref{fig:SC4} top).
These modes were then used as the initialization to find the next mode at $hW_{\text{fixed}} = -1.4$ and so on.
200 steps of gradient ascent were always taken, and learning rates of $2.5 \times 10^-4$ and $5 \times 10^-4$ were used for regimes 1 and 2, respectively.
Each of these modes is denoted $\mathbf{z}^*(hW_{\text{fixed}}, r)$ for regime $r \in \{1, 2\}$.

At each mode, we measure the sensitivity dimension (that of most negative eigenvalue in the Hessian of the EPI distribution) $\mathbf{v}_1(\mathbf{z}^*)$.
To resolve sign degeneracy in eigenvectors, we chose $\mathbf{v}_1(\mathbf{z}^*)$ to have negative element in $hW$.
This tells us what parameter combination rapid task switching is most sensitive to at this parameter choice in the regime.
We see that while the modes of each regime gradually converge to similar connectivites at $hW_{\text{fixed}} = -1.05$ (Fig. \ref{fig:SC4} top), the sensitivity dimensions remain categorically different throughout the two regimes (Fig. \ref{fig:SC4} bottom)
Only at $hW_{\text{fixed}} = -1.05$ is there a flip in sensitivity from regime 2 to regime 1 (in $\mathbf{v}_1(\mathbf{z}^*)_{sW}$ and $\mathbf{v}_1(\mathbf{z}^*)_{hW}$).
There is thus some ambiguity regarding the ``regime" of $\mathbf{z}^*(-1.05, 2)$, since the mode is derived from an initialization in regime 2, but has sensitivity like regime 1.
We can consider this as an intermediate tranisitionary region of parameter space between the two regimes.
To emphasize this, $\mathbf{z}^*(-1.05, 1)$ and $\mathbf{z}^*(-1.05, 2)$ have the same color.

To understand the connectivity mechanisms governing task accuracy, we took the eigendecomposition of the symmetric connectivity matrices $W = Q\Lambda Q^{-1}$, which results in the same basis vectors $\mathbf{q}_i$ for all $W$ parameterized by $\mathbf{z}$ (Fig. \ref{fig:SC3}A). 
These basis vectors have intuitive roles in processing for this task, and are accordingly named the \textit{all} eigenmode - all neurons co-fluctuate, \textit{side} eigenmode - one side dominates the other, \textit{task} eigenmode - the Pro or Anti populations dominate the other, and \textit{diag} mode - Pro- and Anti-populations of opposite hemispheres dominate the opposite pair. 
Due to the parametric structure of the connectivity matrix, the parameters $\mathbf{z}$ are a linear function of the eigenvalues $\bm{\lambda} = [\lambda_{\text{all}}, \lambda_{\text{side}}, \lambda_{\text{task}}\lambda_{\text{diag}}]^\top$ associated with these eigenmodes.
\begin{equation}
\mathbf{z} = A\bm{\lambda}
\end{equation}
\begin{equation}
A = \frac{1}{4} \begin{bmatrix} 1 & 1 & 1 & 1 \\ 1 & -1 & -1 & 1 \\ 1 & 1 & -1 & -1 \\ 1 & -1 & 1 & -1 \end{bmatrix}.
\end{equation}

We are interested in the effect of raising or lowering the amplification of each eigenmode in the connectivity matrix.
To test this, we calculate the the unit vector of changes in the connectivity $\mathbf{z}$ that result form a change in the associated eigenvalues
\begin{equation}
\mathbf{v}_{\text{a}} = \frac{\frac{\partial \mathbf{z}}{\partial \lambda_{\text{a}}}}{|\frac{\partial \mathbf{z}}{\partial \lambda_{\text{a}}}|_2},
\end{equation}
where
\begin{equation} \label{eq:dzdlambda}
\frac{\partial \mathbf{z}}{\partial \lambda_{\text{a}}} = A\mathbf{e}_{\text{a}},
\end{equation}
and e.g. $\mathbf{e}_{\text{all}} = [1, 0, 0, 0]^\top$.
So $\mathbf{v}_{\text{a}}$ is the normalized column of A corresponding to eigenmode $a$.
While perturbations in the sensitivity dimension $\mathbf{v}_1(\mathbf{z}^*)$ adapt with the mode $\mathbf{z}^*$ chosen, perturbations in $\mathbf{v}_a$ for $a \in \{\text{all}, \text{side}, \text{text}, \text{diag}\}$ are invariant to $\mathbf{z}$ (Equation \ref{eq:dzdlambda}).
%
%These eigenvalue changes are evident in the simulations of connectivity perturbations away from the modes (Fig. \ref{fig:SC2}).
%As the component of connectivity along $\mathbf{v}_1$ and $\mathbf{v}_2$ becomes stronger (left-to-right), there is less separation between Pro an Anti populations (lower $\lambda_{\text{task}}$) and greater separation between Left and Right populations following stimulus presentation (greater $\lambda_{\text{side}}$).
%A key differentiating factor is that $\mathbf{v}_1$ substantially increases $\lambda_{\text{diag}}$, while $\mathbf{v}_2$ does not.

We tested whether the inferred SC model connectivites could reproduce experimental effects of optogenetic inactivation in rats \cite{duan2015requirement}.
During periods of simulated optogenetic inactivation, activity was decreased proportional to the optogenetic strength $\gamma$
\begin{equation}
x_\alpha = (1-\gamma)\phi(u_\alpha).
\end{equation}
Delay period inactivation was from $0.8 < t < 1.2$, choice period inactivation was for $t > 1.2$ and total inactivation was for the entire trial.
